Operational Feature Selection in Gaussian Mixture Models

### 2016-09-28 paper.tex
update

    The objective of feature selection is to retrieve the most compact
    representation of  the data with  minimum loss of  information. By
    deleting the  redundant information,  feature selection  allows to
    reduce  dimension  and  thus  avoid  statistical  issue,  increase
    algorithm speed and limit  storage requirements. Moreover, it adds
    several beneficial side effects. It improves data understanding by
    identify where  is the  most relevant information  and it  is then
    possible to save resources when organizing a new data
    acquisition.% TODO: add ref. et example

@@

    \begin{figure}[!t]  %TODO: elle  est  pourrie cette  colorisation!
      % Prend trois bandes dans le visible (RGB) et
      % étire  correctement l'histogramme. De  plus, on ne sait  pas à
      %  quelle  couleur correspond  la  couleur.  Tu devrais  pouvoir
      % récupérer  cela depuis QGIS.  Il faudrait le  rajouter quelque
      % part. J'ai du code TIKZ pour le faire ci-besoin ...
        \centering
        \begin{tabular}{c}
            \includegraphics[width=0.7\columnwidth]{Fig/aisa.png} \\
            {\bfseries{(a)}} \\
            \includegraphics[width=0.7\columnwidth]{Fig/aisa_gt.png} \\
            {\bfseries{(b)}} \\
        \end{tabular}
        \caption{Aisa dataset: {\bfseries{(a)}} colored composition of the image, {\bfseries{(b)}} groundtruth.\label{fig:aisa}}
    \end{figure}

@@

    \begin{table}[!t]
        \centering
        \caption{Results of classification with 1000 samples by class and 5 trials (standard deviation in parenthesis).\label{tab:potsdam-otbsimu}}
        \resizebox{\columnwidth}{!}{%
        \begin{tabular}{|l|c|c|c|c|c|}\hline
             & {\bfseries Kappa of} & {\bfseries Kappa of} & {\bfseries Training} & {\bfseries Classif.} & {\bfseries \# features} \\
             & {\bfseries 5\_11 (train)} & {\bfseries 5\_12 (test)} & {\bfseries time (s)} & {\bfseries time (s)} & {\bfseries to classify} \\ \hline

            GMM SFS kappa & 0.694 (0.002) & 0.669 (0.005) & 400 & 310 & 13.2 \\
            GMM SFS JM &    0.624 (0.028) & 0.631 (0.034) & 2 & 310   & 11 \\
            GMM SFFS JM &   0.624 (0.028) & 0.631 (0.034) & 2.6 & 310   & 11 \\
            GMM ridge &     0.632 (0.007) & 0.592 (0.010) & 10 & 2000 & all \\
            KNN &           0.637 (0.005) & 0.607 (0.005) &  &   & all \\
            Random Forest & 0.729 (0.004) & 0.673 (0.005) & 20 & 840  & all \\

@@

    \begin{table}[!t]
        \centering
        \caption{Results of classification with 50000 samples by class and 5 trials (standard deviation in parenthesis).\label{tab:potsdam-otbsimu-big}}
        \resizebox{\columnwidth}{!}{%
        \begin{tabular}{|l|c|c|c|c|c|}\hline
             & {\bfseries Kappa of} & {\bfseries Kappa of} & {\bfseries Training} & {\bfseries Classif.} & {\bfseries \# features} \\
             & {\bfseries 5\_11 (train)} & {\bfseries 5\_12 (test)} & {\bfseries time (s)} & {\bfseries time (s)} & {\bfseries to classify} \\ \hline

            GMM SFS kappa & 0.713 (0.001) & 0.684 (0.001) & 20000 & 340 & 29 \\
            GMM SFS JM &    0.560 (0.111) & 0.576 (0.104) & 6 & 330 & 10 \\
            GMM SFFS JM &   0.560 (0.111) & 0.576 (0.104) & 6.6 & 340 & 10 \\
            GMM ridge &     0.641 (0.015) & 0.611 (0.026) & 460 & 2000 & all \\
            Random Forest & 0.851 (0.001) & 0.715 (0.001) & 2000 & 2000 & all \\

>>>>

    The objective of feature selection is to retrieve the most compact representation of the data with minimum loss of information \cite{Guyon:2006:FEF:1208773}. By deleting the redundant information, feature selection allows to reduce dimension and thus avoid statistical issue, increase algorithm speed and limit storage requirements. Moreover, it adds several beneficial side effects. It improves data understanding by identify where is the most relevant information and it is then possible to save resources when organizing a new data acquisition.% TODO: add ref. et example

@@

    \begin{figure}[!t]
        \centering
        \begin{tabular}{c}
            \includegraphics[width=0.7\columnwidth]{Fig/aisa.png} \\
            {\bfseries{(a)}} \\
            \includegraphics[width=0.7\columnwidth]{Fig/aisa_gt.png} \\
            {\bfseries{(b)}} \\
        \end{tabular}
        \caption{Aisa dataset: {\bfseries{(a)}} colored composition of the image (R: 634nm, G: 519nm, B: 477nm), {\bfseries{(b)}} groundtruth.\label{fig:aisa}}
    \end{figure}

@@

    \begin{table}[!t]
        \centering
        \caption{Results of classification with 1000 samples by class and 5 trials (standard deviation in parenthesis).\label{tab:potsdam-otbsimu}}
        \resizebox{\columnwidth}{!}{%
        \begin{tabular}{|l|c|c|c||c|c|c|}\hline
             & {\bfseries Kappa of}      & {\bfseries Kappa of}     & {\bfseries Kappa of}     & {\bfseries Training} & {\bfseries Classif.} & {\bfseries \# features} \\
             & {\bfseries 5\_11 (train)} & {\bfseries 5\_12 (test)} & {\bfseries 3\_10 (test)} & {\bfseries time (s)} & {\bfseries time (s)} & {\bfseries to classify} \\
            \hline

            GMM SFS kappa & 0.694 (0.002)             & {\bfseries 0.669 (0.005)} & {\bfseries 0.533 (0.008)} & 400 & 310  & 13.2 \\
            GMM SFS JM &    0.624 (0.028)             & 0.631 (0.034)             & 0.461 (0.027)             & 2   & 310  & 11 \\
            GMM SFFS JM &   0.624 (0.028)             & 0.631 (0.034)             & 0.461 (0.027)             & 2.6 & 310  & 11 \\
            GMM ridge &     0.632 (0.007)             & 0.592 (0.010)             & 0.433 (0.008)             & 10  & 2000 & all \\
            KNN &           0.637 (0.005)             & 0.607 (0.005)             & 0.478 (0.002)             &     &      & all \\
            Random Forest & {\bfseries 0.729 (0.004)} & {\bfseries 0.673 (0.005)} & {\bfseries 0.529 (0.009)} & 20  & 840  & all \\

@@

    \begin{table}[!t]
        \centering
        \caption{Results of classification with 50000 samples by class and 5 trials (standard deviation in parenthesis).\label{tab:potsdam-otbsimu-big}}
        \resizebox{\columnwidth}{!}{%
        \begin{tabular}{|l|c|c|c||c|c|c|}\hline
             & {\bfseries Kappa of}      & {\bfseries Kappa of}     & {\bfseries Kappa of}     & {\bfseries Training} & {\bfseries Classif.} & {\bfseries \# features} \\
             & {\bfseries 5\_11 (train)} & {\bfseries 5\_12 (test)} & {\bfseries 3\_10 (test)} & {\bfseries time (s)} & {\bfseries time (s)} & {\bfseries to classify} \\ \hline

            GMM SFS kappa & 0.713 (0.001) & 0.684 (0.001) & 0.531 (0.005) & 20000 & 340 & 29 \\
            GMM SFS JM &    0.560 (0.111) & 0.576 (0.104) & 0.435 (0.085) & 6 & 330 & 10 \\
            GMM SFFS JM &   0.560 (0.111) & 0.576 (0.104) & 0.435 (0.085) & 6.6 & 340 & 10 \\
            GMM ridge &     0.641 (0.015) & 0.611 (0.026) & 0.440 (0.015) & 460 & 2000 & all \\
            Random Forest & {\bfseries 0.851 (0.001)} & {\bfseries 0.715 (0.001)} & {\bfseries 0.573 (0.002)} & 2000 & 2000 & all \\
